\area{Experience \& Employment}

\entry{Teaching Assistant, Dep. of Mathematics, Stockholm University}
      {2013 Aug -- Ongoing}
      {Currently working as Assistant / Tutor in first-level
       university courses \emph{Mathematics I}, \emph{Mathematics for the Natural Sciences}
       and online course \emph{Introductory Course in Mathematics}.
       The work mainly consists of tutoring students, grading exams, hand-in assignments and
       performing administrative tasks for the department. Part-time employment.}

\entry{Researcher -- Multimedia Technologies, Ericsson Research, Kista}
      {2013 Jun -- 2013 Aug}
      {Working with the latest HTML5 technologies I developed real-time
       web applications for project management, collaboration and productivity.
       This job gained me experience in working in a professional office-environment
       and collaborating within a group of professional software developers.
       See the section 'Programming \& IT' below for a summary of the skill-set I acquired during the summer.
       Full-time employment during the summer.}

\entry{Substitute Teacher -- upper secondary school, Lärarjouren}
      {2012 Sep -- 2013 Jun}
      {At various upper secondary schools I held classes in
       mathematics, physics and the other natural sciences.
       A class was often assigned to me with
       short notice, requiring me to be able to quickly prepare a lecture
       based on the needs of the student group. This job was a great
       opportunity for improving my skills as a group leader and in
       communicating to larger group. Part-time employment.}

\entry{Private Teacher -- upper secondary school, Studybuddy}
      {2012 Aug -- 2013 Jun}
      {I worked one on one with students to achieve the desired knowledge level and
       grades. My role was mainly pedagogical but also coaching and helping
       the student with study techniques and introducing them to higher-level
       education. My subject areas where mainly mathematics and physics but also the
       other natural sciences. The work with a student often extended over a full semester.
       Part-time employment.}

\entry{Student Mentor, Stockholms Universitet}
      {2012 Spring}
      {Student with neuropsychiatric disability, Asperger syndrome.
       Worked regularly with the student, focusing on study techniques,
       setting up concrete goals and planning for the workload and giving
       structure to the studies in general. Part-time during the semester.}
