\area{Programming skills \& IT} % IT \& programming skills
\label{programming}

  A portfolio of some of my most noteworthy open projects can be found on my
  website \href{http://viktorq.se/projects}{viktorq.se/projects}.

\newenvironment{myitemize}{%
  \let\olditem\item
  \renewcommand\item[1][]{\olditem \textbf{##1}\hspace{0.35em}}
  \begin{list}{}{%
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0em}
    \setlength{\parsep}{0.25em}
  }
}{%
  \end{list}
}

\begin{myitemize}

  \item[Web technologies]
    \begin{list}{}{%
      \setlength{\leftmargin}{1.5em}
      \setlength{\itemsep}{0em}
      \setlength{\parskip}{0em}
      \setlength{\parsep}{0.25em}
    }
      \item[Client side]
        I have experience, from both my time at Ericsson Research and from hobby projects,
        in developing responsive, data-intensive applications
        with modern web technologies.

        Experience with MV* frameworks, mainly
        \emph{AngularJS} (favorite) and \emph{Backbone.js}. Layout and design; media queries
        transitions and animations, \emph{Twitter Bootstrap}.

        I get very happy when working
        with real-time collaborative solutions: experience with websockets and \emph{SocketIO}.
      \item[Server side]
        \emph{NodeJS} fanboy. Enjoying \emph{NoSQL} databases such as \emph{mongodb}.
        Liking the mindset of serving data via \emph{REST API} and rendering data on client side
        from AJAX calls --- or websockets depending on the needs.

        Experience in using integrated authentication via \emph{Facebook} and and other authentication
        providers.

        Familiarity with \emph{Ruby on Rails}, \emph{Django}, \emph{PHP} and related services
        and technologies.

        Experience with hosting in the cloud on PaaS'es, mainly working with \emph{Heroku}.
    \end{list}

  \item[Languages]
    \begin{list}{}{%
      \setlength{\leftmargin}{1.5em}
      \setlength{\itemsep}{0em}
      \setlength{\parskip}{0em}
      \setlength{\parsep}{0.25em}
    }
      \item[JavaScript] Currently my favorite language, have written lots of code
        in JS. Also accustomed to CoffeeScript and dialects. See below for
        more details regarding web technologies.
      \item[Python] My first language, currently not coding actively but still very comfortable.
      \item[Bash] Simple scripts and automated system maintenance. See for example my
        \href{https://github.com/ViktorQvarfordt/automated-incremental-backups}{automated backup-system}
        implemented in bash.
      \item[Matlab] Mainly for data analysis, have also explored the object oriented parts Matlab.
      \item[C++] Basic knowledge, one 7.5 ECTS course.
      \item[Misc.] Scheme and dialects of Lisp. Some familiarity (so far mainly fascination) with
        Haskell and other functional languages. Comfortable with Regular Expressions.
    \end{list}

  \item[Numerical methods and analysis] Comfortable implementing numerical methods for solving
    differential equations; Runge Kutta and others. Besides Matlab and Mathematica I have used
    the Python modules SciPy and NumPy, Sage. Experience in statistical analysis of large
    sets of data collected from experiments.

  \item[Misc.]
    \emph{Version management}: Git, Mercurial. \,\,
    \emph{Digital typesetting}: \LaTeX. \,\,
    \emph{Editors}: Emacs, Vim, SublimeText
\end{myitemize}


%% \begin{itemize}
%% \item one \dots{}
%%      \begin{itemize}
%%         \item Language Models
%%         \item Vector Space Models
%%      \end{itemize}
%% \item two \dots{}
%% \item three \dots{}
%% \end{itemize}
